data_cleaning_longer_period

### 2023-08-24 code/analysis_Redo.Rmd
finalize that study sample

```{r}
#dfc <- read_csv("/Users/jhm65/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
```

@@

@@

  df.temp <- df.core[,c(1:9, j, 13:ncol(df.core))]
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )
  did.core <- rbind(did.core, outcomes$coeftable)
}

@@

## Primary effects by distance rival travelled
```{r}
set.seed(123)
df.dist <- df.core %>% 
  left_join(df.z.dist.plot %>% select(`BHCMIS ID.y`, DistToClosestSite), by = c("BHCMIS ID" = "BHCMIS ID.y")) %>% 
  group_by(`BHCMIS ID`) %>% 
  mutate(Dist.random = sample(size = 1, unique(df.z.dist.plot$DistToClosestSite), replace = TRUE), 
         Dist.random = ifelse(Att > 0, DistToClosestSite, Dist.random))

>>>>

```{r}
# dfc <- read_csv("/Users/jhm65/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
# uds.sites.full <- read_csv("/Users/jhm65/Dropbox/Git/Competition/data_processed/sites_geocoded.csv")

@@

df.core2 <- df.core

@@

  df.temp <- df.core[,c(1:9, j, 13:ncol(df.core))]
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )
  did.core <- rbind(did.core, outcomes$coeftable)
}

@@

## Primary effects by distance rival travelled
```{r}
set.seed(123)
df.dist <- df.core2 %>% 
  left_join(df.z.dist.plot %>% select(`BHCMIS ID.y`, DistToClosestSite), by = c("BHCMIS ID" = "BHCMIS ID.y")) %>% 
  group_by(`BHCMIS ID`) %>% 
  mutate(Dist.random = sample(size = 1, unique(df.z.dist.plot$DistToClosestSite), replace = TRUE), 
         Dist.random = ifelse(Att > 0, DistToClosestSite, Dist.random))

### 2023-08-24 code/data_cleaning_longer.Rmd
finalize that study sample

uds.sites.full %>% 
  arrange(`Total Weekly Hours Of Operation`, `Operational Schedule` )
```

@@

# Identify clinics in competitive zip codes
clinics.comp <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
  filter(Year >= included.years[1]) %>%
  select(`BHCMIS ID`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
  group_by(`BHCMIS ID`, Year) %>% 
  summarise(Clinics = max(Clinics)) %>% 
  pivot_wider(id_cols = `BHCMIS ID`, names_from = Year, values_from = Clinics) %>% 
  filter(`2010` == 1 & `2011` == 1) %>%   
  #filter(`2014` == 1 & `2015` == 1) %>%  
  #left_join(chc.term, by = c("BHCMIS ID" = "ClinicID")) %>%
  #filter(is.na(NewClinicID)) %>%
  select(`BHCMIS ID`:`2021`) %>% 
  pivot_longer(cols = c(`2010`:`2021`)) %>% 
  group_by(`BHCMIS ID`) %>% 
  filter(min(value) == 1 ) %>% 
  #filter(max(value) == last(value)) %>% 
  mutate(Tx = ifelse(value > 1, 1, 0))

@@

dfc <- dfc %>% 
  mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6 * 100, 
               CostPerPat = ngla_expense / Total, 
               months_of_cash = as.numeric(months_of_cash),
               quick_ratio = as.numeric(quick_ratio),
               Liquidity = (Assets - Liabilities) / Assets,
               Profitability = ngla_net_gain_loss / Assets, 
               Efficiency = ngla_revenue / Assets,
               NetWorth = (Assets - Liabilities) / Liabilities)

@@

## Write the file
```{r}
#write_csv(dfc, file = "/Users/jhm65/Dropbox/Git/Competition/data_processed/analyticalfile.csv")

>>>>

uds.sites.full %>% 
  arrange(`Total Weekly Hours Of Operation`, `Operational Schedule` )

@@

# Identify clinics in competitive zip codes
clinics.comp <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
  filter(Year >= included.years[1]) %>%
  select(`BHCMIS ID`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
  group_by(`BHCMIS ID`, Year) %>% 
  summarise(Clinics = max(Clinics)) %>% 
  pivot_wider(id_cols = `BHCMIS ID`, names_from = Year, values_from = Clinics) %>% 
  filter(`2010` == 1 & `2011` == 1 ) %>%   
  #filter(`2014` == 1 & `2015` == 1) %>%  
  #left_join(chc.term, by = c("BHCMIS ID" = "ClinicID")) %>%
  #filter(is.na(NewClinicID)) %>%
  select(`BHCMIS ID`:`2021`) %>% 
  pivot_longer(cols = c(`2010`:`2021`)) %>% 
  group_by(`BHCMIS ID`) %>% 
  filter(min(value) == 1 ) %>% 
  #filter(max(value) == last(value)) %>% 
  mutate(Tx = ifelse(value > 1, 1, 0))

@@

dfc <- dfc %>% 
  mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6 * 100, 
         Qcomp.w = (dm.rate * dm.total + htn.rate * htn.total + crc.rate * crc.denom + pap.rate * pap.denom + childbmi.rate * childbmi.denom + adultbmi.rate * adultbmi.denom ) / 
           ( dm.total +  htn.total +  crc.denom +  pap.denom +  childbmi.denom +  adultbmi.denom ) * 100, 
               CostPerPat = ngla_expense / Total, 
               months_of_cash = as.numeric(months_of_cash),
               quick_ratio = as.numeric(quick_ratio),
               Liquidity = (Assets - Liabilities) / Assets,
               Profitability = ngla_net_gain_loss / Assets, 
               Efficiency = ngla_revenue / Assets,
               NetWorth = (Assets - Liabilities) / Liabilities)

@@

## Write the file
```{r}
# write_csv(dfc, file = "/Users/jhm65/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
# write.csv(uds.sites.full, file = "/Users/jhm65/Dropbox/Git/Competition/data_processed/sites_geocoded.csv")
```
